\hi{} and \ovi{} Emission from the Circum-Galactic Medium with a large sample of cosmological hydrodynamical simulations

### 2016-05-20 ms_oviemission.tex
add context about van de Voort (2012)

@@

Absorption line measurements have several limitations. 
Firstly, suitable background sources are rare so that there is 
typically only one or no background sight line per foreground
galaxy({\bf citation}). Because the area covered scales as the 
square of the impact parameter, the resulting measurements 
preferentially probe large impact parameters from foreground 
galaxies.
Finally, because of the 1D nature of absorption line constraints
it is often unclear what physical structure are probed.
Intergral field measurement of emission lines are complementary 
to absorption line measurements.
In particular, they allow us to directly obtain a 3D picture
of the distribution of gas in the CGM by combining the 2D map of
emission on the sky with line-of-sight velocity information.

\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
Feedback in Realistic Environments (FIRE) project.
For each simulation, they predicted the emission from multiple metal lines
including \hi{} and \ovi{}, and found more massive haloes are on average 
more UV-luminous and the UV metal line emission is primarily from collisionally
ionized gas and strongly time variable. The high UV-luminous event correspond
high star formation and \ion{C}{III}, \ion{Si}{III}, \ion{C}{IV} and \ion{Si}{IV}
should be detectable by current and upcoming intergral field spectrographs such
as the Multi Unit Spectroscopic Explorer (MUSE{\bf citation}).

@@

% Multiscale Gaussian Random Fields and Their Application to Cosmological Simulations
%\bibitem[Bertschinger(2001)]{Bertschinger01} Bertschinger, E.\ 2001, 
%\apjs, 137, 1

@@

@@

@@

@@

@@

@@

@@

>>>>

\hi{}  is mainly from cold gas 
($T\approx 10^4$K), and therefore provides an excellent route to 
detecting cold gas in CGM.
In the other hand, most gas in CGM is in the warm or hot phase
with temperature $T > 10^{4.5}$ K, either through photo-ionization,
accretion shock or shock caused by galactic winds \citep{voort12}.
Such dilute halo gas is at $T \sim 10^{4.5-7}$K, 
the detection is dominated by metal lines for Z$>$0.1 Z$_{\odot}$ \citep{Wiersma09a}.

@@

Comparing with Absorption line measurement, in general, 
emission from gas outside of galaxies is to faint to detect.
However, Absorption line measurements have several limitations. 
Firstly, suitable background sources are rare so that there is 
typically only one or no background sight line per foreground
galaxy({\bf citation}). Because the area covered scales as the 
square of the impact parameter, the resulting measurements 
preferentially probe large impact parameters from foreground 
galaxies.
Finally, because of the 1D nature of absorption line constraints
it is often unclear what physical structure are probed.
Intergral field measurement of emission lines are complementary 
to absorption line measurements.
In particular, they allow us to directly obtain a 3D picture
of the distribution of gas in the CGM by combining the 2D map of
emission on the sky with line-of-sight velocity information.

The next generation of spectrographs should be able to detect certain metal
lines, so that several cosmological hydrodynamical simulations have quantified
the expected emission from the warm-hot IGM
\citep{Furlanetto04, Bertone10a, Bertone10b, Takei11, Bertone12,
Frank12, Rocarelli12}.
\citet{Voort13} employed several large cosmological hydrodynamical simulations
from the OverWhelmingly Large Simulations (Owls) project \citep{Schaye10}
to explore the possibility to 
detect metal-line emission if the metallicity Z $>$ 0.1 Z$_\odot$.
They found, at given detection limit, the proposed X-ray telescope and future UV
telescope can detect various metal lines depending on halo mass.
\citet{Sravan15} studied ultra-violet (UV) metal line emission from the CGM
of high-redshift ($z=2-4$) galaxies using cosmological simulations from the 
Feedback in Realistic Environments (FIRE) project.
For each simulation, they predicted the emission from multiple metal lines
including \hi{} and \ovi{}, and found more massive haloes are on average 
more UV-luminous and the UV metal line emission is primarily from collisionally
ionized gas and strongly time variable. The high UV-luminous event correspond
high star formation and \ion{C}{III}, \ion{Si}{III}, \ion{C}{IV} and \ion{Si}{IV}
should be detectable by current and upcoming intergral field spectrographs such
as the Multi Unit Spectroscopic Explorer (MUSE{\bf citation}).

@@

%
\bibitem[Bertone et al.(2010a)]{Bertone10a} Bertone, S., Schaye, J., Dalla Vecchia, C., et al.\ 2010a, \mnras, 407, 544

%
\bibitem[Bertone et al.(2010b)]{Bertone10b} Bertone, S., Schaye, J., Booth, C.~M., et al.\ 2010b, \mnras, 408, 1120

%
\bibitem[Bertone \& Schaye (2012)]{Bertone12} Bertone, S., Schaye, J.\ 2012, \mnras, 419, 780

@@

%
\bibitem[Frank et al.(2012)]{Frank12} Frank, S., et al.\ 2012, \mnras, 420, 1731

@@

%
\bibitem[Furlanetto et al.(2004)]{Furlanetto04} Furlanetto, S.~R., Schaye, J., Springel, V., Hernquist, L.\ 2004, \apj, 606, 221

@@

%
\bibitem[Rocarelli et al.(2012)]{Rocarelli12} Rocarelli, M., Cappelluti, N., Borgani, S., et al.\ 2012, \mnras, 424, 1012

@@

%
\bibitem[Schaye et al.(2010)]{Schaye10} Schaye, J., Dalla Vecchia, C., Booth, C.~M., et al.\ 2010, \mnras, 402, 1536

@@

%
\bibitem[Takei et al.(2011)]{Takei11} Takei, Y., et al.\ 2011, \apj, 734, 91

@@

%
\bibitem[van de Voort \& Schaye (2012)]{voort12} van de Voort, F., Schaye, J.\ 2012, \mnras, 423, 2991

%
\bibitem[van de Voort \& Schaye (2013)]{Voort13} van de Voort, F., Schaye, J.\ 2012, \mnras, 430, 2688

@@

%
\bibitem[Wiersma et al. (2009a)]{Wiersma09a} Wiersma, R.~P.~C., Schaye, J., Smith, B.~D.\ 2009a, \mnras, 393, 99
